### 2024-08-01 getting-started.qmd
20240731 - add raw data files

nfl_players <- progressr::with_progress(
  nflreadr::load_players())
```

@@

```{r}
nfl_players <- nfl_players %>% 
  select(gsis_id, everything()) %>% 
  arrange(display_name)
```

@@

```{r}
nfl_players[nfl_players == ""] <- NA

nfl_players <- nfl_players %>% 
  filter(!is.na(gsis_id))
```

@@

nfl_teams <- progressr::with_progress(
  nflreadr::load_teams(current = TRUE))
```

@@

```{r}
nfl_teams <- nfl_teams %>% 
  select(team_id, everything())
```

@@

nfl_rosters <- progressr::with_progress(
  nflreadr::load_rosters(seasons = TRUE))

nfl_rosters_weekly <- progressr::with_progress(
  nflreadr::load_rosters_weekly(seasons = TRUE))
```

@@

```{r}
nfl_rosters <- nfl_rosters %>% 
  select(gsis_id, season, team, week, everything()) %>% 
  arrange(full_name, gsis_id, season, team, week)
```

@@

```{r}
nfl_rosters_weekly <- nfl_rosters_weekly %>% 
  select(gsis_id, season, week, everything()) %>% 
  arrange(full_name, gsis_id, season, week)
```

@@

nfl_schedules <- progressr::with_progress(
  nflreadr::load_schedules(seasons = TRUE))
```

@@

@@

nfl_combine <- progressr::with_progress(
  nflreadr::load_combine(seasons = TRUE))
```

@@

```{r}
nfl_combine <- nfl_combine %>% 
  select(pfr_id, cfb_id, everything()) %>% 
  arrange(season, player_name)
```

@@

nfl_draftPicks <- progressr::with_progress(
  nflreadr::load_draft_picks(seasons = TRUE))
```

@@

```{r}
nfl_draftPicks <- nfl_draftPicks %>% 
  select(gsis_id, everything()) %>% 
  arrange(pfr_player_name)
```

@@

```{r}
nfl_draftPicks[nfl_draftPicks == ""] <- NA

nfl_draftPicks <- nfl_draftPicks %>% 
  filter(!is.na(gsis_id))
```

@@

nfl_depthCharts <- progressr::with_progress(
  nflreadr::load_depth_charts(seasons = TRUE))
```

@@

```{r}
nfl_depthCharts <- nfl_depthCharts %>% 
  select(gsis_id, season, week, depth_position, everything()) %>% 
  arrange(full_name, gsis_id, season, week, depth_position)
```

@@

nfl_pbp <- progressr::with_progress(
  nflreadr::load_pbp(seasons = TRUE))
```

@@

nfl_pbp <- nflreadr::load_pbp(seasons = TRUE)
```

@@

```{r}
nfl_pbp <- nfl_pbp %>% 
  select(game_id, drive, play_id, everything()) %>% 
  arrange(game_id, drive, play_id)
```

>>>>

nfl_players_raw <- progressr::with_progress(
  nflreadr::load_players())
```

save(
  nfl_players_raw,
  file = "./data/nfl_players_raw.RData"
)
```

load(file = "./data/nfl_players_raw.RData")
```

@@

```{r}
nfl_players <- nfl_players_raw %>% 
  select(gsis_id, everything()) %>% 
  arrange(display_name)
```

@@

```{r}
# Convert missing values to NA
nfl_players[nfl_players == ""] <- NA

# Drop players with missing values for gsis_id
nfl_players <- nfl_players %>% 
  filter(!is.na(gsis_id))
```

@@

nfl_teams_raw <- progressr::with_progress(
  nflreadr::load_teams(current = TRUE))
```

save(
  nfl_teams_raw,
  file = "./data/nfl_teams_raw.RData"
)
```

load(file = "./data/nfl_teams_raw.RData")
```

@@

```{r}
nfl_teams <- nfl_teams_raw %>% 
  select(team_id, everything())
```

@@

nfl_rosters_raw <- progressr::with_progress(
  nflreadr::load_rosters(seasons = TRUE))

nfl_rosters_weekly_raw <- progressr::with_progress(
  nflreadr::load_rosters_weekly(seasons = TRUE))
```

save(
  nfl_rosters_raw,
  file = "./data/nfl_rosters_raw.RData"
)

save(
  nfl_rosters_weekly_raw,
  file = "./data/nfl_rosters_weekly_raw.RData"
)
```

load(file = "./data/nfl_rosters_raw.RData")
load(file = "./data/nfl_rosters_weekly_raw.RData")
```

@@

```{r}
nfl_rosters <- nfl_rosters_raw %>% 
  select(gsis_id, season, team, week, everything()) %>% 
  arrange(full_name, gsis_id, season, team, week)
```

@@

```{r}
nfl_rosters_weekly <- nfl_rosters_weekly_raw %>% 
  select(gsis_id, season, week, everything()) %>% 
  arrange(full_name, gsis_id, season, week)
```

@@

nfl_schedules_raw <- progressr::with_progress(
  nflreadr::load_schedules(seasons = TRUE))
```

save(
  nfl_schedules_raw,
  file = "./data/nfl_schedules_raw.RData"
)
```

load(file = "./data/nfl_schedules_raw.RData")
```

@@

```{r}
nfl_schedules <- nfl_schedules_raw
```

@@

nfl_combine_raw <- progressr::with_progress(
  nflreadr::load_combine(seasons = TRUE))
```

save(
  nfl_combine_raw,
  file = "./data/nfl_combine_raw.RData"
)
```

load(file = "./data/nfl_combine_raw.RData")
```

@@

```{r}
nfl_combine <- nfl_combine_raw %>% 
  select(pfr_id, cfb_id, everything()) %>% 
  arrange(season, player_name)
```

@@

nfl_draftPicks_raw <- progressr::with_progress(
  nflreadr::load_draft_picks(seasons = TRUE))
```

save(
  nfl_draftPicks_raw,
  file = "./data/nfl_draftPicks_raw.RData"
)
```

load(file = "./data/nfl_draftPicks_raw.RData")
```

@@

```{r}
nfl_draftPicks <- nfl_draftPicks_raw %>% 
  select(gsis_id, everything()) %>% 
  arrange(pfr_player_name)
```

@@

```{r}
# Convert missing values to NA
nfl_draftPicks[nfl_draftPicks == ""] <- NA

# Drop players with missing values for gsis_id
nfl_draftPicks <- nfl_draftPicks %>% 
  filter(!is.na(gsis_id))
```

@@

nfl_depthCharts_raw <- progressr::with_progress(
  nflreadr::load_depth_charts(seasons = TRUE))
```

save(
  nfl_depthCharts_raw,
  file = "./data/nfl_depthCharts_raw.RData"
)
```

load(file = "./data/nfl_depthCharts_raw.RData")
```

@@

```{r}
nfl_depthCharts <- nfl_depthCharts_raw %>% 
  select(gsis_id, season, week, depth_position, everything()) %>% 
  arrange(full_name, gsis_id, season, week, depth_position)
```

@@

nfl_pbp_raw <- progressr::with_progress(
  nflreadr::load_pbp(seasons = TRUE))
```

@@

nfl_pbp_raw <- nflreadr::load_pbp(seasons = TRUE)
```

```{r}
save(
  nfl_pbp_raw,
  file = "./data/nfl_pbp_raw.RData"
)
```

load(file = "./data/nfl_pbp_raw.RData")
```

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp_raw.RData", fsep = ""))
```

@@

```{r}
nfl_pbp <- nfl_pbp_raw %>% 
  select(game_id, drive, play_id, everything()) %>% 
  arrange(game_id, drive, play_id)
```
